Higher-Order unification for free!

### 2024-07-01 paper/main.tex
eta expansion -> $\eta$-expansion
real goal -> final goal

Even if we provide an implementation of the object-language unification
\Uo{} in \cref{sec:founif}, our real goal is to simulate the execution of
an entire logic-program.

@@

\begin{definition}[\maybeeta]\label{def:maybeeta}
  \maybeeta is the set of terms $\lambda x.s$ such that $\exists \rho, \rho (\lambda x.s)$
  is an eta expansion. % without the lambda, 5.11 is not true, that
  % is we assume variables are in W
\end{definition}

>>>>

Even if we provide an implementation of the object-language unification
\Uo{} in \cref{sec:founif}, our final goal is to simulate the execution of
an entire logic-program.

@@

\begin{definition}[\maybeeta]\label{def:maybeeta}
  \maybeeta is the set of terms $\lambda x.s$ such that $\exists \rho, \rho (\lambda x.s)$
  is an $\eta$-expansion. % without the lambda, 5.11 is not true, that
  % is we assume variables are in W
\end{definition}
